The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Fix typo.
Write text for steps 78 and 79.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The ource based toolchain installer \candi{}}
\label{subsec:candi}

@@

\item \texttt{step-78} \todo[inline]{TODO}

\item \texttt{step-79} \todo[inline]{TODO}
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The source-based toolchain installer \candi{}}
\label{subsec:candi}

@@

\item \texttt{step-78}, a program written by Tyler Anderson at
  Colorado State University, solves the
  one-dimensional Black-Scholes equations to model the price of stock
  options.

\item \texttt{step-79} is a program for topology optimization. Written
  by Justin O'Connor at Colorado State University, the program asks
  what the optimal distribution of a finite amount of material in a
  domain is to maximize its strength (or optimize some other objective
  functional). It uses advanced optimization techniques.
\end{itemize}
